---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# quanteda.textstat: textual statistics for quanteda

<!-- badges: start -->
[![CRAN Version](https://www.r-pkg.org/badges/version/quanteda.textstat)](https://CRAN.R-project.org/package=quanteda.textstat)
`r badge_devel("quanteda/quanteda.textstat", "royalblue")`
[![Downloads](https://cranlogs.r-pkg.org/badges/quanteda.textstat)](https://CRAN.R-project.org/package=quanteda.textstat)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/quanteda.textstat?color=orange)](https://CRAN.R-project.org/package=quanteda.textstat)
[![R build status](https://github.com/quanteda/quanteda.textstat/workflows/R-CMD-check/badge.svg)](https://github.com/quanteda/quanteda.textstat/actions)
[![codecov](https://codecov.io/gh/quanteda/quanteda.textstat/branch/master/graph/badge.svg)](https://codecov.io/gh/quanteda/quanteda.textstat) [![DOI](https://zenodo.org/badge/5424649.svg)](https://zenodo.org/badge/latestdoi/5424649)
[![DOI](http://joss.theoj.org/papers/10.21105/joss.00774/status.svg)](https://doi.org/10.21105/joss.00774)
<!-- badges: end -->

## About

Contains the textstat functions formerly in **quanteda*8, an R package for managing and analyzing text, created by [Kenneth Benoit](https://kenbenoit.net).
 Supported by the European Research Council grant ERC-2011-StG 283794-QUANTESS.

For more details, see https://quanteda.io.

## How to Install

The normal way from CRAN, using your R GUI or 
```{r eval = FALSE}
install.packages("quanteda.textstat") 
```

Or for the latest development version:
```{r eval = FALSE}
# devtools package required to install quanteda from Github 
devtools::install_github("quanteda/quanteda.textstat") 
```

Because this compiles some C++ and Fortran source code, you will need to have installed the appropriate compilers.

**If you are using a Windows platform**, this means you will need also to install
the [Rtools](https://CRAN.R-project.org/bin/windows/Rtools/) software available
from CRAN.  

**If you are using macOS**, you should install the 
[macOS tools](https://cran.r-project.org/bin/macosx/tools/), 
namely the Clang 6.x compiler and the GNU Fortran compiler (as **quanteda.textstat** requires gfortran to build).  If you are still getting errors related to gfortran, follow the fixes [here](https://thecoatlessprofessor.com/programming/rcpp-rcpparmadillo-and-os-x-mavericks--lgfortran-and--lquadmath-error/).  
    
## How to cite

Benoit, Kenneth, Kohei Watanabe, Haiyan Wang, Paul Nulty, Adam Obeng, Stefan Müller, and Akitaka Matsuo.  (2018) "[quanteda: An R package for the quantitative analysis of textual data](https://www.theoj.org/joss-papers/joss.00774/10.21105.joss.00774.pdf)".  _Journal of Open Source Software_.  3(30), 774. [https://doi.org/10.21105/joss.00774](https://doi.org/10.21105/joss.00774).

For a BibTeX entry, use the output from `citation(package = "quanteda")`.
